Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-27 paper_comparison/paper_comparison/paper_comparison.Rmd
try lme4

@@

>>>>

As discussed in @majumder_validation_2013, individual's skill will affect the number of observers who identify the actual data plot from the lineup. Thus, the power of a visual test depends on the subject-specific abilities. Previously, it was addressed by modelling the probability of a subject $i$ correctly picking the actual data plot from a lineup $l$ using a mixed-effect logistic regression with the subject being treated as a random effect [@majumder_validation_2013]. However, knowing this probability is insufficient to determine the power of a visual test allowed for multiple selections as it doesn't provide information about the number of selections made by the subject, and hence, the p-value can't be computed.

Instead, we modelled the probability of a lineup being rejected directly using a logistic regression with the natural logarithm of the effect size as the only regressor. The same model was applied to different subsets of the survey data to make comparison of the power.

@@

```{r eval = FALSE}
vi_survey_processed %>%
  filter(exp == 3) %>%
  filter(e_sigma != 0.125) %>%
  mutate()

vi_survey_processed %>%
  filter(exp == 3) %>%
  filter(e_sigma != 0.125) %>%
  mutate(set = factor(set), lineup_id = factor(lineup_id)) %>%
  {lme4::glmer(weighted_detect ~ effect_size + ( 0 + effect_size | set) + ( 0 + effect_size | lineup_id), family = binomial ,data = .)} %>%
  predict(type = "response")

  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE)

+
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  ggtitle("poly")

  ?glm
```

### 2022-09-27 paper_comparison/paper_comparison/paper_comparison.tex
try lme4

>>>>

As discussed in \citet{majumder_validation_2013}, individual's skill
will affect the number of observers who identify the actual data plot
from the lineup. Thus, the power of a visual test depends on the
subject-specific abilities. Previously, it was addressed by modelling
the probability of a subject \(i\) correctly picking the actual data
plot from a lineup \(l\) using a mixed-effect logistic regression with
the subject being treated as a random effect
\citep{majumder_validation_2013}. However, knowing this probability is
insufficient to determine the power of a visual test allowed for
multiple selections as it doesn't provide information about the number
of selections made by the subject, and hence, the p-value can't be
computed.

Instead, we modelled the probability of a lineup being rejected directly
using a logistic regression with the natural logarithm of the effect
size as the only regressor. The same model was applied to different
subsets of the survey data to make comparison of the power.
